---
title: "HW5"
author: "Ziqing Wang"
date: "2022-11-13"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
```

## Problem 2
First, import the data as follows.
```{r}
homicide_data = read_csv("./data/homicide-data.csv", skip = 0)
head(homicide_data)
```
The dataset has `r nrow(homicide_data)` observations and `r ncol(homicide_data)` variables. Each observation is a murder case, where the case ID, reported date, victim information (first and last names, race, age, and sex), the physical location of the case (city, state, longitude, and latitude), and a desposition of the case were recorded.  

Proceed with some data processing - First, we create a city-state variable. 
```{r}
homicide_data = homicide_data %>%
  mutate(city_state = str_c(city, state, sep = ", "))
```

Next, we summarize within cities to get the total count of homicides and the total count of unsolved homicides.
```{r}
count_summ = homicide_data %>%
  group_by(city) %>%
  summarize(total_count = n(), # total homicide count by city
            unsolved_count = sum(disposition %in% c("Closed without arrest", "Open/No arrest"))) # total unsolved homicide count by city

count_summ
```
Next we zoom in on the city of Baltimore, MD. We use the prop.test function to estimate the proportion of homicides that were left unsolved and tidy the output:
```{r}
baltimore_summ = count_summ %>%
  filter(city == "Baltimore") 
  
baltimore_proptest_result = prop.test(Baltimore_summ$unsolved_count, baltimore_summ$total_count) %>% 
  broom::tidy() %>%
  select(estimate, conf.low, conf.high) 

baltimore_proptest_result
```
We repeat the operations above for all cities in our dataset.
```{r}
city_proptests = 
  purrr::map2_df(.x = count_summ$unsolved_count,
            .y = count_summ$total_count,
            ~broom::tidy(prop.test(.x, .y))) %>%
  select(estimate, conf.low, conf.high) %>%
  mutate(city = count_summ$city)

city_proptests
```














