---
title: "HW5"
author: "Ziqing Wang"
date: "2022-11-13"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 1 (Provided Solution)
The code chunk below imports the data in individual spreadsheets contained in `./data/q1_data/`. To do this, I create a dataframe that includes the list of all files in that directory and the complete path to each file. As a next step, I `map` over paths and import data using the `read_csv` function. Finally, I `unnest` the result of `map`.

```{r}
full_df = 
  tibble(
    files = list.files("data/q1_data/"),
    path = str_c("data/q1_data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```

The result of the previous code chunk isn't tidy -- data are wide rather than long, and some important variables are included as parts of others. The code chunk below tides the data using string manipulations on the file, converting from wide to long, and selecting relevant variables. 

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

Finally, the code chunk below creates a plot showing individual data, faceted by group. 

```{r individual data by group plot}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

This plot suggests high within-subject correlation -- subjects who start above average end up above average, and those that start below average end up below average. Subjects in the control group generally don't change over time, but those in the experiment group increase their outcome in a roughly linear way. 

## Problem 2: Unsolved homicides in US cities
First, import the data as follows.
```{r}
homicide_data = read_csv("./data/homicide-data.csv", skip = 0)
head(homicide_data)
```
The dataset has `r nrow(homicide_data)` observations and `r ncol(homicide_data)` variables. Each observation is a murder case, where the case ID, reported date, victim information (first and last names, race, age, and sex), the physical location of the case (city, state, longitude, and latitude), and a desposition of the case were recorded.  

Proceed with some data processing - First, we create a city-state variable. 
```{r}
homicide_data = homicide_data %>%
  mutate(city_state = str_c(city, state, sep = ", "))
```

Next, we summarize within cities to get the total count of homicides and the total count of unsolved homicides.
```{r}
count_summ = homicide_data %>%
  group_by(city) %>%
  summarize(total_count = n(), # total homicide count by city
            unsolved_count = sum(disposition %in% c("Closed without arrest", "Open/No arrest"))) # total unsolved homicide count by city

count_summ
```
Next we zoom in on the city of Baltimore, MD. We use the prop.test function to estimate the proportion of homicides that were left unsolved and tidy the output:
```{r}
baltimore_summ = count_summ %>%
  filter(city == "Baltimore") 
  
baltimore_proptest_result = prop.test(Baltimore_summ$unsolved_count, baltimore_summ$total_count) %>% 
  broom::tidy() %>%
  select(estimate, conf.low, conf.high) 

baltimore_proptest_result
```
We repeat the operations above for all cities in our dataset.
```{r}
city_proptests = 
  purrr::map2_df(.x = count_summ$unsolved_count,
            .y = count_summ$total_count,
            ~broom::tidy(prop.test(.x, .y))) %>%
  select(estimate, conf.low, conf.high) %>%
  mutate(city = count_summ$city) %>%
  relocate(city)

city_proptests
```

Below is a plot that shows the estimates and CIs for each city.
```{r unsolved homicides by city plot}
ggplot(city_proptests, 
       aes(x = estimate, y = fct_reorder(city, estimate, .desc=F))) +
  geom_col() +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high)) + 
  labs(title = "Estimated proportion of unsolved homicides by city",
       x = "proportion", y = "city")
```

## Problem 3: Power of the one-sample t-test
First, set the following parameters to be used in simulation.
```{r}
n = 30
sigma = 5
```

Set $\mu = 0$, then generate 5000 datasets from the normal distribution with $\mu = 0$ and $\sigma = 5$. For each dataset, save the estimate $\hat \mu$ and the p-value arising from a test of H: $\mu = 0$ using $\alpha = 0.05$. 
```{r}
mu = 0
sim_results_at_0 = 
  expand_grid(mu = mu, 
              iter = 1:5000) %>%
  mutate(sample = map(.x = mu, ~rnorm(n, .x, sigma))) %>%
  mutate(estimate_df = map(.x = sample, 
                           ~broom::tidy(t.test(.x, 
                                               alternative = "two.sided",
                                               conf.level = 0.95)))) %>%
  unnest(estimate_df) %>%
  select(mu, iter, estimate, p.value)

sim_results_at_0

```

Repeat the follows for $\mu = {1,2,3,4,5,6}$.
```{r}
sim_results = 
  expand_grid(mu = 1:6, 
              iter = 1:5000) %>%
  mutate(sample = map(.x = mu, ~rnorm(n, .x, sigma))) %>%
  mutate(estimate_df = map(.x = sample, 
                           ~broom::tidy(t.test(.x, 
                                               alternative = "two.sided",
                                               conf.level = 0.95)))) %>%
  unnest(estimate_df) %>%
  select(mu, iter, estimate, p.value)

sim_results
```

Below is a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of $\mu$ on the x axis.
```{r power vs effect size plot}
sim_results %>%
  group_by(mu) %>%
  summarize(power = sum(p.value < .05)/n()) %>%
  ggplot(aes(x = mu, y = power)) + geom_point(size = 2) + geom_line() +
  labs(x = "True mean (mu)", y = "power", title = "Power vs. effect size")
```
We can see that power increases with effect size. When the effect size is low, i.e., the true mean $\mu$ is close to 0, the power is low. For instance, when $\mu = 1$, the power is about 0.2. But for $\mu \geq 4$, the power becomes very close to 1.












